Analysis of transit delays in the Toronto Transit Commission: 2024

### 2024-09-26 paper/paper.qmd
Update paper.qmd

>>>>

# Data Visualization
```{r}

```

Figure 1: Distribution of Bus and Streetcar Delay Reasons

Figure 1 illustrates the main reasons for bus and streetcar delays. The primary cause of delays for bus and streetcars are mechanical issues, followed by operational issues, security concerns, diversions, and general delays. Other reasons can be observed in Figure 1, but I will not mention them all as they are not the main causes of delays.

```{r}

```

Figure 2: Distribution of Subway Delay Reasons

Figure 2 illustrates the main reasons for subway delays. The main cause of delays for the subway is patron, injury, incident, and mechanical issues. Other reasons can be observed in Figure 2, but I will not mention them all as they are not the main causes of delays.
